---
title: "About"
description: "Meet the Fridley Lab"
draft: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(purrr)
library(glue)
```

```{r}
links <- list(
  "Brooke Fridley" = list(
    email = "Brooke.Fridley@moffitt.org",
    github = "blfridley",
    link = "https://lab.moffitt.org/fridley/"
  ),
  "Jordan Creed" = list(
    email = "Jordan.H.Creed@moffitt.org",
    github = "jhcreed",
    twitter = "jhcreed"
  ),
  "Chris Wilson" = list(
    email = "Christopher.Wilson@moffitt.org",
    github = "cwilso6"
  )
)
link_images <- list(
  email = "fa fa-envelope-open",
  twitter = "fa fa-twitter",
  github = "fa fa-github",
  link = "fa fa-link"
)
link_prefix <- list(
  email = "mailto:",
  twitter = "https://twitter.com/",
  github = "https://github.com/",
  link = "https://"
)
make_table <- function(name) {
  this_links <- links[[name]]
  if (!length(this_links)) return("")
  rows <- purrr::imap(this_links, ~ glue::glue(
    '<tr>\n<td><i class="{link_images[[.y]]}"></i></td>\n',
    '<td><a href="{link_prefix[[.y]]}{.x}">{.x}</a></td>\n</tr>')
  )
  rows <- paste(rows, collapse = "\n")
  paste(
    '<table style="width: 85%">',
    rows,
    '</table>',
    sep = "\n"
  )
}
headshot_image <- function(img) {
  paste0('<div class="headshot-container"><img class="headshot w90" src="', img, '"></div>')
}
```

:::::: {.row .gutters .about-card}
:::: {.col .col-6}
## Brooke Fridley

`r headshot_image("/img/headshot-fridley.jpg")`

`r make_table("Brooke Fridley")`

::::
:::: {.col .col-6}

Dr. Brooke Fridley's research is in the areas of statistical genomics, molecular epidemiology of cancer, cancer genomics, and pharmacogenomics. 
She has extensive experience as a collaborating statistician, particularly in the design and analysis of studies involving multiple types of ‘omic data.
Recently, she has been particularly involved in molecular epidemiology studies of ovarian cancer, pediatric pharmacogenomic collaborations examining the ontogeny-related metabolomic and transcriptomic changes, and the development of integrative ‘omic analysis methods.
A cross-cutting theme across the lab is the use of R software for data science.
We actively develop and maintain several R packages and user interfaces (e.g., Shiny applications) that aim to alleviate computational bottlenecks associated with conducting molecular epidemiology research.

<!-- For a full list of publications and other academic activities, please see my [complete CV](http://travisgerke.com/cv/). -->

::::
::::::


:::::: {.row .gutters}
:::: {.col .col-6 .about-card}
## Jordan Creed

`r headshot_image("/img/headshot-creed.png")`

`r make_table("Jordan Creed")`

Jordan is a Research Data Analyst working in the domains of statistics, bioinformatics and epidemiology. 
Her current work focuses on the molecular epidemiology of prostate and brain cancer.

::::

:::: {.col .col-6 .about-card}
## Chris Wilson

`r headshot_image("/img/headshot-wilson.png")`

`r make_table("Chris Wilson")`

Chris is awesome! 

::::
::::::